### 2016-05-23 TreeLevel.tex
new plots

\subsection{Partonic Cross Sections}
Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross sections (see Appendix \ref{sec:cross_section}) via
\begin{align}
\frac{\mbox{d}^2 \sigma^B}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2
\end{align}
The leading order cross sections are
\begin{align}
\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
&+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma^B(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
\sigma^B(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma^B(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
& + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{27(m_-^4 + m_{\tilde{q}}^2s)} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
\sigma^B(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
\sigma^B(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
\end{align}
where the abbreviations 
\begin{align}
&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
\end{align}
are used\cite{Beenakker:1996ch}.

@@

\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
This process is exactly the same in the MSSM and MRSSM.

\subsection{Hadronic Cross Section}
factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)\\
The hadronic cross section for the production of a final state $X$, e.g. $X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
\begin{align}
\sigma^B_{\mathrm{Had}}(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B_{\mathrm{Part}} (ij \to X, s = x_ 1x_2 S).
\end{align}
As the production of the final state $X$ may proceed with various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
\begin{align}
\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(i,j \to X).
\end{align}
To get an intuitive idea of the factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark. In addition there are gluons and seaquarks, i.e. virtual quark-antiquark pairs.} which are permanently interacting which each other. Now consider two colliding hadrons in their center-of-mass frame. Due to Lorentz contraction the hadrons appear as thin discs. Furthermore the parton's mutual interactions are time-delayed. This effectively means that a hadron at the time of collision is virtually frozen.\\
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.45]{figures/MRSSM:q+q->sq+sq_mr=2_seperated}
\caption{Hadronic cross section for squark production in the MRSSM at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 1.5. The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}. As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
\end{center}
\end{figure}
refer to paper in Peskin on how to get pdf's
\\
refer to Kribs, Martin
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors expect for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}. As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
\end{center}
\end{figure}

discussion of channels, maybe copy from above\\
refer to Vernoica Sanz: How many SUpersymmetries?

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.6]{figures/contour_MRSSM_squarks}
\caption{}
\end{center}
\end{figure}

>>>>

\subsection{Partonic Cross Sections}
Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross sections (see Appendix \ref{sec:cross_section}) via
\begin{align}
\frac{\mbox{d}^2 \sigma^B}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}^B|^2
\end{align}
The leading order cross sections are
\begin{align}
\sigma^B(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
&+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma^B(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
\sigma^B(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma^B(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
& + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{27(m_-^4 + m_{\tilde{q}}^2s)} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
\sigma^B(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
\sigma^B(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
\end{align}
where the abbreviations \cite{Beenakker:1996ch} 
\begin{align}
&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
\end{align}
are used. The comparison of the cross sections of the MRSSM with those of the MSSM is postponed until the next subsection where the confinement of quarks and gluons within hadrons is accounted for.

\subsection{Hadronic Cross Section}
factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)\\
Quarks, anti-quarks and gluons are no free particles but are confined within hadrons. As hadrons consist of a variety of the just mentioned partons which share the hadron's momentum one does not have a definite initial state which is assumed in the previous subsection. Fortunately the hadronic cross section for the production of a final state $X$, e.g. $X = \tilde{q} \tilde{q}$, can be obtained by convolving the partonic cross section with the parton density functions of the initial partons.
\sigma^B_{\mathrm{Had}}(P_1 P_2 \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_{P_1/H_1}(x_1) f_{P_2/H_2}(x_2)\ \sigma^B_{\mathrm{Part}} (P_1 P_2 \to X, s = x_ 1x_2 S).
As the production of the final state $X$ may proceed via various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(P_1 P_2 \to X).
To get an intuitive idea of this factorization consider the hadrons as extended objects consisting of partons\footnote{The proton is considered as composed of three valence quarks: Two up-quarks and one down-quark. In addition there are gluons and seaquarks, i.e. virtual quark-antiquark pairs.} which are permanently interacting which each other. Now consider two colliding hadrons in their center-of-mass frame. Due to Lorentz contraction the hadrons appear as thin discs and the parton's mutual interactions are time-delayed within this frame. This effectively means that a hadron at the time of collision is virtually frozen.\\
maybe picture of colliding disks\\
This in turn implies that the hadron consists at the time of collision of a definite number of partons which can be thought of as carrying a definite fraction of the hadron's momentum $p_{\mathrm{Part}} = x p_{\mathrm{Had}}$ with $x \in \left(0, 1 \right)$. The parton density function $f_{P/H}(x)$ can therefore be understood as the probability of finding a parton $P$ within the hadron $H$ carrying $x$ of its momentum. See ...(refer to paper in Peskin on how to get pdf's)... for how to ascertain parton density functions\\
Fig. ... shows a parton density function set for the proton. One can see that the partons most probable to carry a high fraction of momentum are the valence quarks. For lower values of $x$ gluons constitute the major component of the proton.\\
\begin{figure}[!htpb]
\includegraphics[scale=.45]{figures/MRSSM:q+q->sq+sq_mr=2_seperated}
\caption{Hadronic cross section for squark production in the MRSSM at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 1.5. The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}. As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}
Fig.\ref{fig:TreeXsection} shows the hadronic cross section for the production of various squarks. These can only be produced by their supersymmetric partner, e.g. two up-squarks can only be produced by two up-quarks. One therefore sees the influence of the parton distribution functions quite nicely: The up-squark production is the dominant contribution to squark production. Apart from the solid lines in fig.\ref{fig:TreeXsection} which correspond to the production of first generation squarks, also the cross section of mixed first and second generation (dashed lines) and second generation squarks is shown. The dashed dotted line shows the cross section of the charged conjugated particles of the dominant channel.\\
refer to Kribs, Martin
\begin{figure}[!htpb]
\includegraphics[scale=.4]{figures/mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.4]{figures/mr=2_MSSM+MRSSM}
\caption{Hadronic cross section for squark and gluino production in the MSSM (left-hand side) and MRSSM (right-hand side) at the LHC at $\sqrt{S} = \unit[13]{GeV}$. The ratio of gluino and squark mass is fixed to 0.9 (first row) and 2 (second row). In the final state it has been summed over all squark flavors expect for staus. For the channels $qq \to \tilde{q}\tilde{q}$ and $qG \to \tilde{q}\tilde{G}$ also the charge conjugated process is included. The parton densities used are $\mathtt{MMHT2014}$ LO with $\alpha_s(M_Z) = 0.135$ in the 5-flavor scheme \cite{Harland-Lang:2014zoa}. As renormalization and factorization scale $\mu_R = \mu_F = \frac{m_1 + m_2}{2}$ has been chosen, where $m_i$ are the final state particle masses.} \label{fig:TreeXsection}

@@

\subsubsection*{The process $q G \to \tilde{q} \tilde{g}$}
This process is exactly the same in the MSSM and MRSSM.
\\
refer to Vernoica Sanz: How many SUpersymmetries?

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.6]{figures/contour_MRSSM_squarks}
\includegraphics[scale=.6]{figures/contour_MSSM_squarks}
\caption{}
\end{center}
\end{figure}

\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.5]{figures/MSSM+MRSSM_msg=2000}
\includegraphics[scale=.5]{figures/MSSM+MRSSM_msq=1000}
\caption{add error bars}
\end{center}
\end{figure}

### 2016-05-23 Virt_Real.tex
new plots

\section{Virtual and Real Corrections}
This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order. The $\mathcal{O}(\alpha_s)$ correction to the tree level process includes the computation of one-loop diagrams such as shown in fig. ???. To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered. However the virtual amplitude 
\begin{align}
\mathcal{M}^{\mathrm{V}} = \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} = 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)
\end{align}
contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops. Due to their origin these divergences are referred to as ultraviolet and infrared divergences.
Ultraviolet divergences occur when the loop momentum tends to infinity which corresponds to arbitrary short distance interactions. However, these divergences are cured by first regularizing them and then introducing appropriate counterterms in the Lagrangian to cancel the extracted singularities. The second step is called renormalization and can be understood as a redefinition or rescaling of parameters and fields in the Lagrangian in the first place. This procedure will be discussed in detail in section \label{sec:renMRSSM}.\\
Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at the cross section. However, this is not finite as it comprises infrared divergences. These split into soft and collinear (or mass) singularities\footnote{The names differ in the literature. Often infrared divergences are used as a synonym for soft divergences.} which cannot be removed by means of renormalization.

Naunberg

\subsection{Virtual Correction}

>>>>

\section{Virtual and Real Corrections}
The results calculated in the previous chapter are not the full theoretical predictions for the different processes but only the first term in a perturbation theory of $\alpha_s$.\\
This section describes the necessary steps in the calculation of the squark production cross section at next-to-leading-order, i.e. its $\mathcal{O}(\alpha_s)$-correction.\\
Reason validity of perturbation theory in this context.

\subsection{Virtual Correction}
According to quantum field theory the $\mathcal{O}(\alpha_s)$ correction to a tree level process includes the computation of one-loop diagrams such as shown in fig. ???. To yield $\mathcal{O}(\alpha_s)$ corrections in the cross section the interference term between the one-loop amplitude $\mathcal{M}^{\mathrm{1L}}$ and the Born amplitude $\mathcal{M}^{\mathrm{B}}$ needs to be considered. However the virtual amplitude 
\begin{align}
\mathcal{M}^{\mathrm{V}} = \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} + \mathcal{M}^{\mathrm{1L}} \mathcal{M}^{\mathrm{B}\ast} = 2 \Re \left( \mathcal{M}^{\mathrm{B}} \mathcal{M}^{\mathrm{1L}\ast} \right)
\end{align}
contains divergences. These come from integrals over undetermined momentum and energy of particles running in loops. Due to their origin these divergences are referred to as ultraviolet and infrared divergences.
Ultraviolet divergences occur when the loop momenta and energy tend to infinity which corresponds to arbitrary short distance interactions. However, these divergences are cured by first regularizing them and then introducing appropriate counterterms\footnote{These counterterms have to be of the same $\mathcal{O}(\hbar)$ as the loop diagrams they are constructed to cancel. NOCHMAL IN LAHIRI / PAL NACHSCHAUEN.} in the Lagrangian to cancel the extracted singularities. The second step is called renormalization and can be understood as a redefinition or rescaling of parameters and fields in the Lagrangian in the first place:
\begin{align}
\tilde{q}_{L/R} \to \sqrt{Z_{\tilde{q}_{L/R}}} \tilde{q}_{L/R}\\
...
\end{align}
This procedure will be discussed in detail in section \label{sec:renMRSSM}.\\
Having removed the ultraviolet divergences one performs the 2-body phase space integration to arrive at an ultraviolet-finite cross section. However, this cross section is not free of divergences as it comprises infrared divergences. These split into soft and collinear (or mass) singularities\footnote{The names differ in the literature. Often infrared divergences are used as a synonym for soft divergences.} which cannot be removed by means of renormalization.

\subsection{Real Corrections}
Kinoshita-Lee-Naunberg-Theorem\\
At the end: scheme of real and virtual corrections from WARB-talk
